Evaluation

### 2018-04-13 evaluation.Rmd
Continue to get latest data from portalr (following update in PortalData versioning scheme)

# Setup rodent observations
species_abundance = portalr::abundance("repo", shape='flat', level='treatment', 
                                       length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  rename(actual = abundance, level = treatment) %>%
  mutate(level='Controls',currency='abundance') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance("repo", shape='flat', level='treatment', 
                                     length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  group_by(newmoonnumber) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total')

>>>>

# Setup rodent observations
species_abundance = portalr::abundance("repo", clean=FALSE, shape='flat', level='treatment', 
                                       length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  rename(actual = abundance, level = treatment) %>%
  mutate(level='Controls',currency='abundance') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance("repo", clean=FALSE, shape='flat', level='treatment', 
                                     length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  group_by(newmoonnumber) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total')
